Assessing primitives performance\\ on multi-stage execution

### 2018-05-09 paper.tex
add methodology. detailed table incoming

\todo{fill methodology section}
\cba{missing here: what are the benchmark actually run ? Can be short code sample or explanation of both. It has to include: each bench was run x times, each time being y comparison. We removed the loop overhead in the measurements.}
\cba{+ we bench only = strings, which could make a difference on the plugin version (one less branch) - maybe we should change to number of character compared instead of string size so it does not imply the string are equals.}
\cba{SM methodology: what is done? which benchmarks are used? how are they executed? what is measured? how do you address warmup etc? what kind of machine is used for the measurements?}

>>>>

We assessed the execution time of the different implementations by running the following benchmark:

\begin{code}
Smalltalk garbageCollect.
#(0 1 5 100 1000) collect: [ :size |
	| iterations time overhead |
	collection := ByteString new: size.
	collection2 := ByteString new: size.
	size < 100 ifTrue: [iterations := (100000000 // (size*10 max: 1) sqrt) floor.]
			   ifFalse: [iterations := (10000000 // size sqrt) floor.].
	overhead := [ 1 to: iterations do: [ :i | ] ] timeToRun.
	time := [ 1 to: iterations do: [ :i | 
		collection compareWithSlang: collection2 ] ] timeToRun.
	stream nextPutAll: ((time - overhead) asString)].
\end{code}\\

Each benchmark was measured 30 times.

In each benchmark, we run a string comparison in a loop and measure the total execution time.
The number of iterations of the loop depends on the string size: the comparison is repeated between 1414 and 10000 times for a short string (5 characters or less), and between 100 and 316 times for a long string (100 characters or more). This addresses the warm-up of the JIT and allows the benchmarks to run at least 1 second in the slower implementations.
The loop overhead is measured and removed from the measurements.

\cba{+ we bench only = strings, which could make a difference on the plugin version (one less branch) - maybe we should change to number of character compared instead of string size so it does not imply the string are equals.}
